Timeliness of security updates for Android

### 2014-02-18 securityupdates.tex
Daniel T. Wagner rather than Daniel Wagner

\author{Daniel R.\ Thomas, Daniel Wagner, Alastair R.\ Beresford and Andrew Rice}

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Daniel R.\ Thomas,
Daniel Wagner,
Alastair R.\ Beresford,
Andrew Rice}
\IEEEauthorblockA{
Computer Laboratory\\
University of Cambridge\\
Cambridge, United Kingdom\\
Firstname.Lastname@cl.cam.ac.uk
}
}

>>>>

\author{Daniel R.\ Thomas, Daniel T.\ Wagner, Alastair R.\ Beresford and Andrew Rice}

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Daniel R.\ Thomas,
Daniel T.\ Wagner,
Alastair R.\ Beresford,
Andrew Rice}
\IEEEauthorblockA{
Computer Laboratory\\
University of Cambridge\\
Cambridge, United Kingdom\\
Firstname.Lastname@cl.cam.ac.uk
}
}
